Applying Automated Verification to Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-04-26 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated text ASE

While some research efforts exist to enhance and optimize the software development processes for CPS, more investigation and discussion of better and more effective models is needed [Al-Jaroodi]. Among the opportunities for enhancements there is the developing new techniques and tools to support CPS requirements gathering and analysis. The developed techniques need to be able to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS. In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, can be dealed with formal verification~\cite{NESSI}. Energy production, distribution, and optimization are all CPS problems~\cite{UC}.

@@

Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of systems~\cite{ClarkeHV18}. Therefore, in the context of this proposal, a cyber-physical system, specifically a PV system, is the target. We review verification tools and related them to design and to verify PV systems, which was uncommon in prior studies~\cite{abs-1811-09438}.

The main contribution of this approach is to allow that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the system, and the algorithm using automated verification, and written in language C, can find the best compromise between those two objectives (power reliability and system cost).

\textcolor{red}{We need to make our contributions stronger. Why the SE community would be interested in this paper? What are the main open problems we need them to solve here? Remember that this is a paper for new ideas... we don't need to make questions but we don't need to answer all of them.}

%, using non-deterministic variables and exploring the design-space
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Verification}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate three state-of-the-art model checkers to formally optimize the sizing of PV designs w.r.t. user requirements.

@@

Regarding power reliability, the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean? Remember that we have software engineering audience}.

However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC). Here, one more time, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.

>>>>

While some research efforts exist to enhance and optimize the software development processes for CPS, more investigation and discussion of better and more effective models is needed~\cite{Al-Jaroodi2016}. Among the opportunities for enhancements there is the developing new techniques and tools to support CPS requirements gathering and analysis. The developed techniques need to be able to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS. In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, can be dealed with formal verification~\cite{NESSI}. Energy production, distribution, and optimization are all CPS problems~\cite{UC}.

@@

Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of systems~\cite{ClarkeHV18}. %Therefore, in the context of this proposal, a CPS, specifically a PV system, is the target. We review verification tools and related them to design and to PV systems verification, which was uncommon in prior studies~\cite{abs-1811-09438}.

\textcolor{red}{The main contributions of this approach is (1) to address a CPS, allowing that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the system together with user requirements and environment constraints, and the algorithm using automated verification, written in language C, can find the best compromise between two objectives: power reliability and system cost, i.e., linking the optimum solution in technical and economical terms; and (2), to evaluate different state-of-art software verifiers in order to obtain the better performance. The use of automated verication in electrical systems was uncommon in prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented.}
%
%\textcolor{red}{We need to make our contributions stronger. Why the SE community would be interested in this paper? What are the main open problems we need them to solve here? Remember that this is a paper for new ideas... we don't need to make questions but we don't need to answer all of them.}
%
%, using non-deterministic variables and exploring the design-space
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Verification}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate three state-of-the-art model checkers to formally optimize the sizing of PV designs w.r.t. user requirements.

@@

Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}.
%the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean? Remember that we have software engineering audience}.

However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC). Here, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
